### 2021-01-27 ch04_papers_ecs_tcr_assessment/papers_ecs_tcr_assessment.tex
Updated several figures
Adapted copyright statements

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/gregory_regression_cmip6_mmm.pdf}
  \caption{Gregory regression for the \acs{CMIP}6 \acf{MMM} following
    \textcite{Gregory2004}: Global and annual mean net \acl{TOA} radiation $N$
    versus the change in global and annual mean near-surface air temperature
    $\Delta T$ for 150 years of a simulation with an abrupt quadrupling of the
    atmospheric \acs{CO2} concentration (\nxcotwo{4}) for the \acs{CMIP}6
    \acs{MMM} (circles). To account for energy leakage and model drift, a
    linear fit of the corresponding pre-industrial control run is subtracted
    from the \nxcotwo{4} simulation. A linear regression can be used to
    calculate the \acf{ECS} according to \cref{eq:02:ecs} with the radiative
    forcing $F_\text{4x}$ (\yintercept) and the climate feedback parameter
    $\lambda$ (slope) for all 150 years (black line), which results in
    $\text{ECS} = 3.74 \unit{K}$. Due to non-linear effects, the exact value
    of \acs{ECS} depends on the years considered for the Gregory regression
    (see \cref{subsec:02:ecs} and
    \cref{fig:02:gregory_regression_different_years}): Using only the first 20
    years of the simulation (blue circles and line) yields a considerably
    smaller \acs{ECS} than using only the last 130 years of the simulation
    (orange circles and line). Updated from \textcite{Meehl2020}.}
  \label{fig:04:gregory_regression_cmip6_mmm}
\end{figure}

\begin{table}[!t]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP5_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{\acf{ECS} and \acf{TCR} evaluated for the \acs{CMIP}5 models.
    Details on the calculation of \acs{ECS} and \acs{TCR} are given in
    \cref{subsec:02:ecs} and \cref{subsec:02:tcr}, respectively. The \acf{MMM}
    is calculated from the Gregory regression method using the \acs{MMM} net
    \acf{TOA} radiation and the \acs{MMM} change in \acf{GSAT} similar to
    \cref{fig:04:gregory_regression_cmip6_mmm}. The multi-model standard
    deviation is given by the sample standard deviation of \acs{ECS} evaluated
    over all climate models (using the normalization $1 / M$, where $M$ is the
    number of models).}
  \label{tab:04:ecs_tcr_cmip5}
\end{table}

\begin{table}[p]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP6_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{As in \cref{tab:04:ecs_tcr_cmip5} but for the \acs{CMIP}6 models.}
  \label{tab:04:ecs_tcr_cmip6}
\end{table}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/historical_ecs_tcr_ranges.pdf}
  \caption{Assessed values of the \acf{ECS} (blue bars) and the \acf{TCR} (red
    bars) over the years in the Charney report from 1979 \autocite{Charney1979}
    and the subsequent \acfp{AR} of the \acf{IPCC} \autocite{Mitchell1990,
      Kattenberg1996, Albritton2001, Solomon2007, Stocker2013}. Orange and
    green bars represent the modeled ranges of \acs{ECS} and \acs{TCR},
    respectively, from the different climate model ensembles of the \acf{CMIP}
    with the corresponding \acf{MMM} illustrated with the horizontal black
    lines (the green dot represents output from a single climate model). The
    numbers correspond to individual \acs{CMIP}5 and \acs{CMIP}6 models (see
    \cref{tab:04:ecs_tcr_cmip5,tab:04:ecs_tcr_cmip6}). Updated from
    \textcite{Meehl2020}.}
  \label{fig:04:historical_ecs_tcr_ranges}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_netcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:a}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_netcre-cmip5_netcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:b}
  \end{subfigure}
  \\
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_swcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:c}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_swcre-cmip5_swcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:d}
  \end{subfigure}
  \\
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_lwcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:e}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{\SmallSubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_lwcre-cmip5_lwcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:f}
  \end{subfigure}
  \caption{Geographical distributions of the net (a), shortwave (c) and
    longwave (e) \acf{CRE} feedback parameters for the \acs{CMIP}6 \acf{MMM}
    and the corresponding differences to the \acs{CMIP}5 \acs{MMM}, again for
    the net (b), shortwave (d) and longwave (f) components. The \acs{CRE}
    feedback parameters for each grid cell are calculated with a Gregory
    regression of the grid cell's \acs{CRE} versus the change in the
    \acl{GSAT} (see \cref{subsec:02:cloud_feedback_parameters}). Updated from
    \textcite{Bock2020}.}
  \label{fig:04:cloud_feedback_parameters}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/gregory_regression_cmip6_mmm.pdf}
  \caption{Gregory regression for the \acs{CMIP}6 \acf{MMM} following
    \textcite{Gregory2004}: Global and annual mean net \acl{TOA} radiation $N$
    versus the change in global and annual mean near-surface air temperature
    $\Delta T$ for 150 years of a simulation with an abrupt quadrupling of the
    atmospheric \acs{CO2} concentration (\nxcotwo{4}) for the \acs{CMIP}6
    \acs{MMM} (circles). To account for energy leakage and model drift, a
    linear fit of the corresponding pre-industrial control run is subtracted
    from the \nxcotwo{4} simulation. A linear regression can be used to
    calculate the \acf{ECS} according to \cref{eq:02:ecs} with the radiative
    forcing $F_\text{4x}$ (\yintercept) and the climate feedback parameter
    $\lambda$ (slope) for all 150 years (black line), which results in
    $\text{ECS} = 3.74 \unit{K}$. Due to non-linear effects, the exact value
    of \acs{ECS} depends on the years considered for the Gregory regression
    (see \cref{subsec:02:ecs} and
    \cref{fig:02:gregory_regression_different_years}): Using only the first 20
    years of the simulation (blue circles and line) yields a considerably
    smaller \acs{ECS} than using only the last 130 years of the simulation
    (orange circles and line). \AdaptedFrom{Meehl2020}.}
  \label{fig:04:gregory_regression_cmip6_mmm}
\end{figure}

\begin{table}[!t]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP5_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{\acf{ECS} and \acf{TCR} evaluated for the \acs{CMIP}5 models.
    Details on the calculation of \acs{ECS} and \acs{TCR} are given in
    \cref{subsec:02:ecs} and \cref{subsec:02:tcr}, respectively. The \acf{MMM}
    is calculated from the Gregory regression method using the \acs{MMM} net
    \acf{TOA} radiation and the \acs{MMM} change in \acf{GSAT} similar to
    \cref{fig:04:gregory_regression_cmip6_mmm}. The multi-model standard
    deviation is given by the sample standard deviation of \acs{ECS} evaluated
    over all climate models (using the normalization $1 / M$, where $M$ is the
    number of models). \AdaptedFrom{Meehl2020}.}
  \label{tab:04:ecs_tcr_cmip5}
\end{table}

\begin{table}[p]
  \centering
  \csvreader[ECSAndTCRTable]{
    ch04_papers_ecs_tcr_assessment/data/CMIP6_ecs-tcr.csv}{}{
    \dataset & \idx & \ecs & \tcr}
  \caption{As in \cref{tab:04:ecs_tcr_cmip5} but for the \acs{CMIP}6 models.
    \AdaptedFrom{Meehl2020}.}
  \label{tab:04:ecs_tcr_cmip6}
\end{table}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch04_papers_ecs_tcr_assessment/figs/historical_ecs_tcr_ranges.pdf}
  \caption{Assessed values of the \acf{ECS} (blue bars) and the \acf{TCR} (red
    bars) over the years in the Charney report from 1979 \autocite{Charney1979}
    and the subsequent \acfp{AR} of the \acf{IPCC} \autocite{Mitchell1990,
      Kattenberg1996, Albritton2001, Solomon2007, Stocker2013}. Orange and
    green bars represent the modeled ranges of \acs{ECS} and \acs{TCR},
    respectively, from the different climate model ensembles of the \acf{CMIP}
    with the corresponding \acf{MMM} illustrated with the horizontal black
    lines (the green dot represents output from a single climate model). The
    numbers correspond to individual \acs{CMIP}5 and \acs{CMIP}6 models (see
    \cref{tab:04:ecs_tcr_cmip5,tab:04:ecs_tcr_cmip6}).
    \AdaptedFrom{Meehl2020}.}
  \label{fig:04:historical_ecs_tcr_ranges}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_netcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_netcre-cmip5_netcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:b}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_swcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:c}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_swcre-cmip5_swcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:d}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/abs_cmip6_lwcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:e}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch04_papers_ecs_tcr_assessment/figs/bias_cmip6_lwcre-cmip5_lwcre.pdf}
    \caption{}
    \label{fig:04:cloud_feedback_parameters:f}
  \end{subfigure}
  \caption{Geographical distributions of the net (a), shortwave (c) and
    longwave (e) \acf{CRE} feedback parameters for the \acs{CMIP}6 \acf{MMM}
    and the corresponding differences to the \acs{CMIP}5 \acs{MMM}, again for
    the net (b), shortwave (d) and longwave (f) components. The \acs{CRE}
    feedback parameters for each grid cell are calculated with a Gregory
    regression of the grid cell's \acs{CRE} versus the change in the
    \acl{GSAT} (see \cref{subsec:02:cloud_feedback_parameters}).
    \AdaptedFrom{Bock2020}.}
  \label{fig:04:cloud_feedback_parameters}
\end{figure}
